Preliminary Draft

### 2021-07-29 article/draft.tex
updates in YT section

To analyse the collected data, we ranked the recommended videos based on the number of times they got recommended. We then asked Science Feedback to fact-check the top 40 recommended videos, which amounts to $16\%$ of the data. Six videos (10.5\%) out of the top $40$ recommended videos were marked as misleading. This relatively small percentage points towards that idea that, YouTube is likely reducing the visibility of videos containing misinformation or alternatively maybe there is little misinformation on YouTube. Also it might be that the experiment setup did not influence the behavior of the recommendation engine, since we start with a single YouTube video marked as ``False'' every time. We further examined the top recommended channels in the collected data. We got $1$ $562$ different channels, and we counted the number of times every channel got recommended. Figure \ref{channels_yt} shows the top $10$ recommended channels, whose videos represent $30\%$ of the total set of recommended videos in our dataset. The top most recommended channel is Fox News, which has a ``mixed'' factual reporting level according to $iffy.news$ and has several failed fact-checks.\footnote{See \href{https://mediabiasfactcheck.com/fox-news-bias/}{https://mediabiasfactcheck.com/fox-news-bias/}.} Also in the top ten most recommended, there are two channels with a ``low'' factual reporting level: PrgerU and Sky news Australia.

\begin{figure}[h]
	\begin{center}
		\includegraphics[scale=0.5]{./img/channel_youtube.png} 
	\end{center}
	\caption{Top ten recommended channels.}
	\label{channels_yt}
\end{figure}

>>>>

To analyse the collected data, we ranked the recommended videos based on the number of times they got recommended. We then asked Science Feedback to fact-check the top 40 recommended videos, which amounts to $16\%$ of the data. Six videos (10.5\%) out of the top $40$ recommended videos were marked as misleading. This relatively small percentage points towards that idea that, YouTube is likely reducing the visibility of videos containing misinformation or alternatively maybe there is little misinformation on YouTube. Also it might be that the experiment setup did not influence the behavior of the recommendation engine, since we start with a single YouTube video marked as ``False'' every time. We further examined the top recommended channels in the collected data. We got $1$ $562$ different channels, and we counted the number of times every channel got recommended. Figure \ref{channels_yt} shows the top $10$ recommended channels, whose videos represent $30\%$ of the total set of recommended videos in our dataset. Among the top three most recommended channels, there is Fox News and Sky News Australia, which both have a ``mixed'' factual reporting level according to $iffy.news$ and have several failed fact-checks.\footnote{See \href{https://mediabiasfactcheck.com/fox-news-bias/}{https://mediabiasfactcheck.com/fox-news-bias/} and \href{https://mediabiasfactcheck.com/sky-news-australia/}{https://mediabiasfactcheck.com/sky-news-australia/}.} Also in the top ten most recommended, we find PragerU, which has a ``low'' level of factual reporting according to iff.news.

\begin{figure}[h]
	\begin{center}
		\includegraphics[scale=0.6]{./img/channel_youtube.png} 
	\end{center}
	\caption{Top ten recommended channels.}
	\label{channels_yt}
\end{figure}
